Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-15 paper/tex/analysis.tex
moving Scotts Rule and resizing excessively large figures
moving content

To the knowledge of the authors, there is only one metric that can be used to evaluate the performance of individual \pzpdf\ estimators in the absence of true \pz\ posteriors.
Using the notation introduced in Section~\ref{sec:flexzboost}, the conditional density estimation (CDE) loss is defined as
\begin{equation}
  \label{eq:cde-loss}
  L(f, \widehat{f}) \equiv \int \int (f(z \vert \x) - \widehat{f}(z \vert \x))^{2} dz dP(\x)
\end{equation}
in terms of the photometry $\x$, an analogue to the familiar root-mean-square-error used in conventional regression.
We estimate the CDE loss via
\begin{equation}
  \label{eq:estimated-cde-loss}
  \hat{L}(f, \widehat{f}) = \mathbb{E}_\X \left[\int \widehat{f}(z \mid \X)^{2} dz\right] - 2 \mathbb{E}_{\X, Z}\left[\widehat{f}(Z \mid \X)\right] + K_{f},
\end{equation}
where the first term is the expectation value of the \pz\ posterior with respect to the marginal distribution of the photometric covariates $\X$, the second term is the expectation value with respect to the joint distribution of $\X$ and the space $Z$ of all possible redshifts, and the third term $K_{f}$ is a constant depending only upon the true conditional densities $f(z \vert \x)$.
We may estimate these expectations empirically on the test or validation data \citep[Eq.~7 in][]{Izbicki:17b} without knowledge of the true densities.

@@

Though alternatives exist \citep{Malz:chippr}, ``stacking'' according to
\begin{equation}
  \label{eq:stacked}
  \hat{N}^{H}(z) \equiv \frac{1}{N_{tot}}\ \sum_{i}^{N_{tot}}\ \hat{p}^{H}_{i}(z)
\end{equation}
is the most widely accepted method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$.
Though we do not endorse the use of the stacked estimator of the redshift distribution, we use it under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.

>>>>

The \buzz\ simulation process precludes testing the degree to which samples from our \pz\ posteriors reconstruct the space of $p(z, {\rm data})$.
To the knowledge of the authors, there is only one metric that can be used to evaluate the performance of individual \pzpdf\ estimators in the absence of true \pz\ posteriors.
Using the notation introduced in Section~\ref{sec:flexzboost}, the conditional density estimation (CDE) loss is defined as
\begin{equation}
  \label{eq:cde-loss}
  L(f, \widehat{f}) \equiv \int \int (f(z \vert \x) - \widehat{f}(z \vert \x))^{2} dz dP(\x)
\end{equation}
in terms of the photometry $\x$, an analogue to the familiar root-mean-square-error used in conventional regression.
We estimate the CDE loss via
\begin{equation}
  \label{eq:estimated-cde-loss}
  \hat{L}(f, \widehat{f}) = \mathbb{E}_\X \left[\int \widehat{f}(z \mid \X)^{2} dz\right] - 2 \mathbb{E}_{\X, Z}\left[\widehat{f}(Z \mid \X)\right] + K_{f},
\end{equation}
where the first term is the expectation value of the \pz\ posterior with respect to the marginal distribution of the photometric covariates $\X$, the second term is the expectation value with respect to the joint distribution of $\X$ and the space $Z$ of all possible redshifts, and the third term $K_{f}$ is a constant depending only upon the true conditional densities $f(z \vert \x)$.
We may estimate these expectations empirically on the test or validation data \citep[Eq.~7 in][]{Izbicki:17b} without knowledge of the true densities.

@@

Though alternatives exist \citep{Malz:chippr}, ``stacking'' according to
\begin{equation}
  \label{eq:stacked}
  \hat{N}^{H}(z) \equiv \frac{1}{N_{tot}}\ \sum_{i}^{N_{tot}}\ \hat{p}^{H}_{i}(z)
\end{equation}
is the most widely accepted method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$.
Though we do not endorse the use of the stacked estimator of the redshift distribution, we use it under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.
In addition, very few scientific use cases will employ the overall $\hat{N}(z)$ with no cuts, as we explore in this paper.
We discuss in Section~\ref{sec:futurework} variants of the stacked estimator, such as realistic tomographic binning schemes, that will be explored in future work.

### 2019-03-15 paper/tex/results.tex
moving content

We remind the reader that contributed codes were given a goal of obtaining accurate \pzpdf s, not an accurate stacked estimator of the redshift distribution, so we do not expect the same codes to necessarily perform well for both classes of metrics.
As previously stated, there are a variety of scientific use cases for \pz s, and metric-specific relative performance implies that we may need multiple \pzpdf\ approaches tuned to each metric in order to maximize returns over all science cases in large upcoming surveys.

Samples from accurate photo-$z$ posteriors should reproduce the space of $p(z,{\rm data})$.
However, it is difficult to test this reconstruction given our data set, as the galaxy distributions arise from mock objects pasted on to an underlying dark matter halo catalogue with properties designed to match empirical relations, rather than being drawn from statistical distributions in redshift.
In previous sections we have mentioned that optimizing for a specific metric does not guarantee good performance on other metrics, nor is there any guarantee that good performance by our metrics corresponds to \textit{accurate} photo-$z$ posteriors, in the sense of predicting redshifts for individual galaxies.
%\aim{Explain that samples from accurate photo-$z$ posteriors should reconstruct the space of $p(z, data)$, a test we can't check with our datasets.}
In other words, we can construct photo-$z$ estimators that provide good coverage in many of our tests, but which have very little predictive power.

>>>>

We remind the reader that contributed codes were given a goal of obtaining accurate \pzpdf s, not an accurate stacked estimator of the redshift distribution, so we do not expect the same codes to necessarily perform well for both classes of metrics.
In previous sections we have mentioned that optimizing for a specific metric does not guarantee good performance on other metrics, nor are our metrics able to assess the fidelity of individual \pzpdf s relative to true posteriors.
As previously stated, there are a variety of scientific use cases for \pz s, and metric-specific relative performance implies that we may need multiple \pzpdf\ approaches tuned to each metric in order to maximize returns over all science cases in large upcoming surveys.

%\aim{Explain that samples from accurate photo-$z$ posteriors should reconstruct the space of $p(z, data)$, a test we can't check with our datasets.}
In other words, we can construct photo-$z$ estimators that provide good coverage in many of our tests, but which have very little predictive power.
